Fermi and eROSITA bubbles: A proof-of-concept study

### 2021-12-19 paper.tex
update

  The plane-parallel potential is fixed throughout our simulations and given by
  \begin{equation}
    \Phi_{\text{total}}(z) = \Phi_{\text{bulge}}(z) + \Phi_{\text{halo}}(z),
  \end{equation}
  where
  \begin{equation}
    \Phi_{\text{bulge}}(z)=\
    2\sigma^2_{\text{bulge}}\
    \ln\cosh\left(z\sqrt{\frac{2\pi G\rho_{\text{bulge}}^{\text{peak}}}{\sigma^2_{\text{bulge}}}}\right)
  \end{equation}
  is the potential of an isothermal slab mainly contributed by stars around the Galactic plane, and\
  $\Phi_{\text{halo}}(z)=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right)$\
  is a plane-parallel dark logarithmic halo potential.

  With the help of the isothermal and hydrostatic equilibrium conditions,\
  we can write the steady-state gaseous density distributions of disk and the Galactic atmosphere\
  that are in pressure equilibrium and\
  confined in the total potential, $\Phi_{\text{total}}$, as\
  \begin{equation}
     \rho(z)=
     \begin{cases}
     \displaystyle\rho_{\text{disk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{disk}}/m_{\text{p}}}\right] & \text{, if $|z| < z_{0}$}\\
     \\
     \displaystyle\rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{atmp}}/m_{\text{p}}}\right] & \text{, otherwise,}
     \end{cases}
  \end{equation}
  where $m_{\text{p}}$ is a proton mass,\
  $T_{\text{disk}}$ and $T_{\text{atmp}}$ is the temperature of the disk and the atmosphere,\
  $\rho_{\text{disk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
  of the disk and atmosphere on the mid-plane $z=0$.

  All parameters are listed in \Cref{table-parameters}, except for $\rho_{\text{atmp}}^{\text{peak}}$ that\
  can be derived from the known parameters and pressure equilibrium condition\
  on the interfaces $(z=\pm z_{0})$ between disk and atmosphere.

  \Cref{density-profile} shows the initial density profile of hot halo for the simulation presented here.\

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table*}[t]
\centering
\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrr@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                                             & Description                   & Value                          & Reference                       \\ \midrule
{\bf Disk }\citep{peak-ism-density}                   &                               &                                &                                 \\
$z_{0}$                                               & Scale height of disk          & 100 pc                         &                                 \\
$T_{\text{\text{disk}}}$                              & Temperature of disk           & $10^{3}$ K                     &                                 \\
$\rho_{\text{disk}}^{\text{peak}}$                    & Peak mass density of disk     & $10^{-23}$ g/cm$^{3}$          &                                 \\ \hline
{\bf Atmosphere }\citep{temperature-MW}               &                               &                                &                                 \\
$T_{\text{\text{atmp}}}$                              & Temperature of atmosphere     & $10^{6}$ K                     &                                 \\ \hline
{\bf Static stellar potential }                       &                               &                                &                                 \\
$\sigma_{\text{bulge}}$                               & Velocity dispersion of bulge  & 100 km/s                       & \citep{velocity-dispersion-MW}  \\
$\rho_{\text{bulge}}^{\text{peak}}$                   & Peak average density of bulge & $4\times 10^{-24}$ g/cm$^{3}$  &                                 \\ \hline
{\bf Static dark halo potential }\citep{Johnston1995} &                               &                                &                                 \\
$v_{\text{halo}}$                                     &                               & 131.5 km/s                     &                                 \\
$d_{\text{h}}$                                        & Core radius                   & 12 kpc                         &                                 \\ \midrule
\end{tabular}
\end{table*}

>>>>

  The plane-parallel potential is fixed throughout our simulations and given by
  \begin{equation}
    \Phi_{\text{total}}(z) = \Phi_{\text{bulge}}(z) + \Phi_{\text{halo}}(z),
  \end{equation}
  where
  \begin{equation}
    \Phi_{\text{bulge}}(z)=\
    2\sigma^2_{\text{bulge}}\
    \ln\cosh\left(z\sqrt{\frac{2\pi G\rho_{\text{bulge}}^{\text{peak}}}{\sigma^2_{\text{bulge}}}}\right)
  \end{equation}
  is the potential of an isothermal slab mainly contributed by stars around the Galactic bulge, and\
  $\Phi_{\text{halo}}(z)=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right)$\
  is a plane-parallel dark logarithmic halo potential.

  With the help of the isothermal and hydrostatic equilibrium conditions,\
  and assuming the disk and atmosphere is in pressure equilibrium,\
  we can write the steady-state gaseous density distributions of disk and the Galactic atmosphere\
  confined in the total potential, $\Phi_{\text{total}}$, as\
  \begin{equation}
     \rho(z)=
     \begin{cases}
     \displaystyle\rho_{\text{disk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{disk}}/m_{\text{p}}}\right] & \text{, if $|z| < z_{0}$}\\
     \\
     \displaystyle\rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{atmp}}/m_{\text{p}}}\right] & \text{, otherwise,}
     \end{cases}
  \end{equation}
  where $m_{\text{p}}$ is a proton mass,\
  $T_{\text{disk}}$ and $T_{\text{atmp}}$ is the temperature of the disk and the atmosphere,\
  $\rho_{\text{disk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
  of the disk and atmosphere on the mid-plane $z=0$.

  We tabulate all parameters in \Cref{table-parameters}, except for $\rho_{\text{atmp}}^{\text{peak}}$ that\
  can be derived from the known parameters and pressure equilibrium condition\
  on the interfaces $(z=\pm z_{0})$ between disk and atmosphere.\

  The initial density profile based on the above construction is shown in \Cref{density-profile}\
  and compared to the observed result beyond 1 kpc \citep{Miller_2013}.\

  Note that there is an difficulty in disentangling the contribution\
  of the Local Bubble, a supernova remnant in which the Solar System is embedded \citep{Snowden1990},\
  and the contribution from solar wind charge-exchange processes, which produce soft\
  X-ray emission throughout the Solar System. As a result, the density profile of the Galactic halo remains unclear\
  \citep{BlandHawthorn2016}.

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table*}[t]
\centering
\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrr@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                                             & Description                   & Value                          & Reference                       \\ \midrule
{\bf ISM Disk }\citep{peak-ism-density}                   &                               &                                &                                 \\
$z_{0}$                                               & Scale height of disk          & 100 pc                         &                                 \\
$T_{\text{\text{disk}}}$                              & Temperature of disk           & $10^{3}$ K                     &                                 \\
$\rho_{\text{disk}}^{\text{peak}}$                    & Peak mass density of disk     & $10^{-23}$ g/cm$^{3}$          &                                 \\ \hline
{\bf Atmosphere }\citep{temperature-MW}               &                               &                                &                                 \\
$T_{\text{\text{atmp}}}$                              & Temperature of atmosphere     & $10^{6}$ K                     &                                 \\ \hline
{\bf Static stellar potential }                       &                               &                                &                                 \\
$\sigma_{\text{bulge}}$                               & Velocity dispersion of bulge  & 100 km/s                       & \citep{velocity-dispersion-MW}  \\
$\rho_{\text{bulge}}^{\text{peak}}$                   & Peak average density of bulge & $4\times 10^{-24}$ g/cm$^{3}$  &                                 \\ \hline
{\bf Static dark halo potential }\citep{Johnston1995} &                               &                                &                                 \\
$v_{\text{halo}}$                                     &                               & 131.5 km/s                     &                                 \\
$d_{\text{h}}$                                        & Core radius                   & 12 kpc                         &                                 \\ \midrule
\end{tabular}
\end{table*}
